Flowchart of Current Algorithm

### 2008-10-12 docs/flowchart/paper.tex
switch over to a latex description for the individual steps

%--------------------------------------------------------------------------
% STEP 1
%--------------------------------------------------------------------------
\noindent {\bf Step 1.} {\em Define the average expansion at time $t^\nph$ and the new $w_0.$}

@@

%--------------------------------------------------------------------------
% STEP 2
%--------------------------------------------------------------------------
\noindent {\bf Step 2.} {\em Construct the provisional edge-based advective velocity}, $\uadvone$.\\

@@

%--------------------------------------------------------------------------
% STEP 3
%--------------------------------------------------------------------------
\noindent {\bf Step 3.} {\em React the full state through the first time interval of $\dt / 2.$}

@@

%--------------------------------------------------------------------------
% STEP 4
%--------------------------------------------------------------------------
\noindent {\bf Step 4.} {\em Advect the base state, then the full state, through a time interval of $\dt.$}

@@

%--------------------------------------------------------------------------
% STEP 5
%--------------------------------------------------------------------------
\noindent {\bf Step 5.} {\em React the full state through a second time interval of $\dt / 2.$}

@@

%--------------------------------------------------------------------------
% STEP 6
%--------------------------------------------------------------------------
\noindent {\bf Step 6.} {\em Define a new average expansion rate at time $t^\nph.$}

@@

%--------------------------------------------------------------------------
% STEP 7
%--------------------------------------------------------------------------
\noindent {\bf Step 7.} {\em Construct the final edge-based advective velocity}, $\uadvtwo$:

@@

%--------------------------------------------------------------------------
% STEP 8
%--------------------------------------------------------------------------
\noindent {\bf Step 8.} {\em Advect the base state, then the full state, through a time interval of $\dt.$}

@@

%--------------------------------------------------------------------------
% STEP 9
%--------------------------------------------------------------------------
\noindent {\bf Step 9.} {\em React the full state through a second time interval of $\dt / 2.$}

@@

%--------------------------------------------------------------------------
% STEP 10
%--------------------------------------------------------------------------
\noindent {\bf Step 10.} {\em Compute $S^{n+1}$ for the final projection.}

@@

%--------------------------------------------------------------------------
% STEP 11
%--------------------------------------------------------------------------
\noindent {\bf Step 11.} {\em Update the velocity}.

@@

%--------------------------------------------------------------------------
% STEP 12
%--------------------------------------------------------------------------
\noindent {\bf Step 12.} {\em Compute a new $\dt.$}

@@

>>>>

%--------------------------------------------------------------------------
% STEP 1
%--------------------------------------------------------------------------

\begin{description}

\item[Step 1.] {\em Define the average expansion at time $t^\nph$ and the new $w_0.$}

@@

%--------------------------------------------------------------------------
% STEP 2
%--------------------------------------------------------------------------
\item[Step 2.] {\em Construct the provisional edge-based advective velocity}, $\uadvone$.\\

@@

%--------------------------------------------------------------------------
% STEP 3
%--------------------------------------------------------------------------
\item[Step 3.] {\em React the full state through the first time interval of $\dt / 2.$}

@@

%--------------------------------------------------------------------------
% STEP 4
%--------------------------------------------------------------------------
\item[Step 4.] {\em Advect the base state, then the full state, through a time interval of $\dt.$}

@@

%--------------------------------------------------------------------------
% STEP 5
%--------------------------------------------------------------------------
\item[Step 5.] {\em React the full state through a second time interval of $\dt / 2.$}

@@

%--------------------------------------------------------------------------
% STEP 6
%--------------------------------------------------------------------------
\item[Step 6.] {\em Define a new average expansion rate at time $t^\nph.$}

@@

%--------------------------------------------------------------------------
% STEP 7
%--------------------------------------------------------------------------
\item[Step 7.] {\em Construct the final edge-based advective velocity}, $\uadvtwo$:

@@

%--------------------------------------------------------------------------
% STEP 8
%--------------------------------------------------------------------------
\item[Step 8.] {\em Advect the base state, then the full state, through a time interval of $\dt.$}

@@

%--------------------------------------------------------------------------
% STEP 9
%--------------------------------------------------------------------------
\item[Step 9.] {\em React the full state through a second time interval of $\dt / 2.$}

@@

%--------------------------------------------------------------------------
% STEP 10
%--------------------------------------------------------------------------
\item[Step 10.] {\em Compute $S^{n+1}$ for the final projection.}

@@

%--------------------------------------------------------------------------
% STEP 11
%--------------------------------------------------------------------------
\item[Step 11.] {\em Update the velocity}.

@@

%--------------------------------------------------------------------------
% STEP 12
%--------------------------------------------------------------------------
\item[Step 12.] {\em Compute a new $\dt.$}

@@

\end{description}
